

%!TEX root = ./main.tex
%\clearpage
%\null
%\vfil
%---------- FORMAT -----------------------------------------------------------
\clearpage 
\begin{center}
	\textbf{Acknowledgments} 
\end{center}

At this place, I would like to thank some of the persons who supported me during the entire process of working on this thesis.

At first, I am deeply grateful to Dominik Schatzmann and Dr. Bernhard Ager for their support, their great expertise and their patience in explaining me even basics concepts. 
They always asked the right questions at the right time, thus directing my focus on the important things. 
During the last half year, they have always provided good remarks and excellent advisory -- not only regarding technical aspects. 
I really enjoyed our discussions and the process of working with them. 

Furthermore, I would like to express my sincere gratitude to Prof. Dr. Bernhard Plattner for providing me the opportunity to write this thesis in his research group and his excellent remarks. 

In addition, I enjoyed the support of the entire Computer Engineering Group (CSG) in various situations. In particular, I am grateful to Brian Trammell for always providing me the required support regarding the computing infrastructure in a very pleasant manner. 

Finally, I am very thankful to my close friends for motivating and supporting me in all circumstances.

%---------- FORMAT -----------------------------------------------------------
\vspace{1cm} Daniel Aschwanden 
\vfil
%---------- END -----------------------------------------------------------