%!TEX root = ./main.tex
\chapter{Conclusion\label{Conclusion}}

\section{Conclusion}
Adjusting the traffic preselection of FACT from a port-based heuristic to a 
server socket based approach is far more than just a generalization. 

On the one hand, the server sockets approach is less affected by scanning and 
p2p, acting as a kind of history based scanning filter. Thus, reducing the 
negative effect of malware and p2p churn on the network outage detection. 

On the other hand, a smart composition of the server socket set used for the 
detection process may generally increase the observation coverage of FACT 
without significantly increasing the noise ratio. Hence, the practical usability 
of FACT is increase even more.

The drawback of the approach is clearly that additional resources are required 
to store the server sockets and the additional effort to detect, monitor and 
characterize the server sockets. 
Nevertheless, the good results from chapter \ref{chapter:results} indicates that 
server sockets are quite stable over time and that there are even good results 
possible for events in March, May and August 2010 with sockets detected in 
November 2010. 

However, the selection of server sockets can be cumbersome and directly 
influences the detection sensitivity of FACT. Though, even without any 
optimization the server socket approach is clearly outperforming the original port-based heuristic with respect to the \emph{event-to-noise} ratio. 

\section{Future Work}
% characterize ses by time based activity (night / day, working week, weekend etc.)

In the future, new characterization methods can be investigated, especially the 
visibility allows to define different metrics, as day / night periods, working 
week activity or weekend activity. These new metrics would allow to characterize 
a server socket even more detailed. Thus, getting a better view on the different 
properties of these sockets. 

% smarter socket set selection => density of network by choosing only the popularst sockets of each network
Furthermore, the server socket set selection can be further enhanced by 
different techniques. On the one hand, the density of server socket per 
prefix/network should be considered and examined. By deducing the number of 
sockets required per network so that the probability of seeing traffic towards 
this network is maximized. This would be clearly dependent on the single 
visibility of the selected sockets within this network. Moreover, the general 
optimization problem can be mathematically expressed by defining an objective 
function. This optimization problem may then be solved by different approaches 
as simulated annealing or integer linear programming. In addition, the effect of 
the number of sockets of a set should be considered. 

% consider different selection methods as clustering analysis approaches, e.g. k-means etc => distance function include also network considerations.. etc. 
On the other hand, different selection approaches can be examined as well. Given 
the problem scope of the socket selection based on different characteristics, 
clustering analysis approaches are worth to be considered. 

% automatization of process => danger of excluding sockets affected by events
% => consider full last week?  
Up to now, the process of detecting, monitoring and characterizing server sockets is entirely independent from FACT, therefore, an integration of these processing chains into FACT should be considered. However, there is the danger of not selecting good sockets during potential events affecting these networks. Hence, good approaches should not considering the (network) event periods by characterizing individual server sockets.

% near future public release of FlowBox and FACT
Finally, the FlowBox library and the FACT source code are intended to be released to public in the very near future, licensed under the Gnu Public License v3. 